Ampersand uses Relation Algebra as Programming Language

### 2017-07-20 2017 JLAMP/articleRamics.tex
Fixed antiquotations, so this file produces valid LaTeX.

\begin{abstract}
	Relation Algebra can be used as a programming language for building information systems.
	This paper demonstrates the principle by presenting a case study together with the theory behind programming in Relation Algebra.
	As a case study, we have developed a database-application for legal reasoning.
	We discuss a small part of it to illustrate the mechanisms of programming in Relation Algebra.
	Beside being declarative, relation algebra comes with attractive promises for developing big software.
	The compiler that was used for this case study, Ampersand, is the result of an open source project.
	Ampersand has been tried and tested in practice and is available as free open source software\footnote{\tt https://github.com/AmpersandTarski/Ampersand}.
	This article is an extended version of a conference paper presented at RAMiCS-2017 \cite{Joosten2017}.
\end{abstract}

@@

>>>>

\begin{abstract}
	Relation Algebra can be used as a programming language for building information systems.
	This paper demonstrates the principle by presenting a case study together with the theory behind programming in Relation Algebra.
	As a case study, we have developed a database-application for legal reasoning.
	We discuss a small part of it to illustrate the mechanisms of programming in Relation Algebra.
	Beside being declarative, relation algebra comes with attractive promises for developing big software.
	The compiler that was used for this case study, Ampersand, is the result of an open source project.
	Ampersand has been tried and tested in practice and is available as free open source software\footnote{\tt https://github.com/AmpersandTarski/Ampersand}.
	This article is an extended version of a conference paper presented at RAMiCS-2017 \cite{JoostenRAMiCS2017}.
\end{abstract}

@@

	The similarity with the reactive programming paradigm~\cite{Bainomugisha2013} is obvious from figure~\ref{fig:event flow}.
	This graph is part of the program graph as conceived in reactive programs.
	The code fragments described in section~\ref{sct:Code Fragments}
	might be generated towards a mature reactive programming language (e.g. ELM)
	and executed directly.
	Ampersand lets you think in constraints and (reactive) code fragments to preserve invariants can be generated with the theory in this paper.
	Currently Ampersand generates towards classical PHP+HTML+JavaScript code,
	but generation to a reactive programming language (e.g. ELM) is definitely on the wishlist.
